\begin{thebibliography}{}
\bibitem[Kö]{}
\textsc{Bernhard Köck}, ``Belyi's Theorem Revisited'', arXiv:math.AG/0108222, 2001.
\bibitem[Kö2]{}
\textsc{Bernhard Köck}, ``Belyi's Theorem Revisited'', Beiträge zur Algebra und Geometrie, Volume \textbf{45}, 2004.
\bibitem[Ha]{Hartshorne}
\textsc{R. Hartshorne}, ``Algebraic Geometry'', Graduate Texts in Mathematics \textbf{52}, Springer-Verlag, New York 1977.
\bibitem[Fo]{Forster}
\textsc{O. Forster}, ``Lectures on Riemann Surfaces'', Graduate Texts in Mathematics \textbf{81}, Springer-Verlag, New York 1981.
\bibitem[Bo]{bosch}
\textsc{S. Bosch}, ``Algebra'', 4. Auflage, Springer-Verlag, Berlin 2001.
\bibitem[Wi]{}
\textsc{D. J. Winter}, ``The Structure of Fields'', Graduate Texts in Mathematics \textbf{16}, Springer-Verlag, New York 1974.
\bibitem[Ma]{}
\textsc{H. Matsumura}, ``Commutative algebra'', Second Edition, Mathematics lecture note series \textbf{56}, The Benjamin/Cumming Publishing Co., 1980.
\bibitem[Hal]{Hall}
\textsc{M. Hall}, ``The theory of groups'', Second Edition, Macmillian Co., New York 1968.
\bibitem[Bb]{bour}
\textsc{N. Bourbaki}, ``Algebra I'', Chapters 1-3, Elements of Mathematics, Addison-Wesley Publishing Co., Great Britain 1973.
\bibitem[EH]{}
\textsc{D. Eisenbud, J. Harris}, ``The Geometry of Schemes'', Graduate Texts in Mathematics \textbf{197}, Springer-Verlag, New York 2000.
\bibitem[Lüt]{}
\textsc{W. Lütkebohmert}, ``Codierungstheorie'', 1. Auflage, Vieweg, 2003.
\bibitem[Wa]{}
\textsc{F. Warner}, ``Foundations of Differentiable Manifolds and Lie Groups'', Graduate Texts in Mathematics \textbf{94}, Springer-Verlag, New York 1983.
\bibitem[SZ]{Zieschang}
\textsc{R. Stöcker, H. Zieschang}, ``Algebraische Topologie'', Mathematische Leitfäden, B. G. Teubner, Stuttgart 1988.
\end{thebibliography}
